---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

[![stability-unstable](https://img.shields.io/badge/stability-unstable-yellow.svg)](https://github.com/joethorley/stability-badges#unstable)
[![Travis-CI Build Status](https://travis-ci.org/poissonconsulting/poisdata.svg?branch=master)](https://travis-ci.org/poissonconsulting/poisdata)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/poissonconsulting/poisdata?branch=master&svg=true)](https://ci.appveyor.com/project/poissonconsulting/poisdata)
[![Coverage Status](https://img.shields.io/codecov/c/github/poissonconsulting/poisdata/master.svg)](https://codecov.io/github/poissonconsulting/poisdata?branch=master)
[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg)](https://opensource.org/licenses/MIT)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/poisdata)](https://cran.r-project.org/package=poisdata)

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# poisdata

An R package to read and write data for Poisson Consulting scripts and packages.

## Demonstration

```{r demonstration}
library(poisdata)

read_hobo_csv(system.file("hobo", "10723440.csv", package = "poisdata"))
```

## Installation

`poisdata` is available from GitHub
```
# install.packages("devtools")
devtools::install_github("poissonconsulting/poisdata")
```

or the Poisson R Archive Site ([PoisRAS](https://github.com/poissonconsulting/drat))
```
# install.packages("drat")
drat::addRepo("poissonconsulting")
install.packages("poisdata")
```
## Contribution

Please report any [issues](https://github.com/poissonconsulting/poisdata/issues).

[Pull requests](https://github.com/poissonconsulting/poisdata/pulls) are always welcome.

Please note that this project is released with a [Contributor Code of Conduct](https://github.com/poissonconsulting/poisdata/blob/master/CONDUCT.md). 
By participating in this project you agree to abide by its terms.
